\bf The Right Arm Bias in ITF Taekwon-Do \\ Patterns Chon-Ji to Juche

### 2012-02-26 article.tex
Fixed wording in the abstract

  When performing patterns in ITF Taekwon-Do, one of the factors mentioned in
  the condensed Encyclopedia is that there should be an equal number of
  techniques to both sides of the body. Here we analyze hand techniques in
  Chon-Ji through Juche to establish whether or not there is a bias towards
  either side.  This is done by attaching metadata, in the form of tags, to
  each pattern movement. These tags are extracted from each movement's English
  description in the Encyclopedia, and supplemented with keywords noted while
  performing the pattern. We then apply concepts from set theory to retrieve
  the information we are interested in, and find that there are seven more
  techniques on the right side than on the left.

>>>>

  When performing patterns in ITF Taekwon-Do, one of the factors mentioned in
  the condensed Encyclopedia is that there should be an equal number of
  techniques to both sides of the body. Here we analyze hand techniques in
  Chon-Ji through Juche to establish whether or not there is a bias towards
  either side.  This is done by attaching metadata, in the form of tags, to each
  pattern movement. These tags are generated from the Encyclopedia's description
  of the movements, and supplemented by keywords that were identified by
  carefully examining each pattern. We then apply concepts from set theory to
  retrieve the information we are interested in, and find that there are seven
  more techniques on the right side than on the left.
